The development of infants' responses to mispronunciations: A Meta-Analysis

### 2020-07-07 VonHolzenBergmann_MPMetaAnalysis.tex
revision and resubmission to Dev Psych

\abstract{
As they develop into mature speakers of their native language, infants must not only learn words but also the sounds that make up those words. To do so, they must strike a balance between accepting speaker dependent variation (e.g.~mood, voice, accent), but appropriately rejecting variation when it (potentially) changes a word's meaning (e.g.~cat vs.~hat). This meta-analysis focuses on studies investigating infants' ability to detect mispronunciations in familiar words, or mispronunciation sensitivity. Our goal was to evaluate the development of infants' phonological representations for familiar words as well as explore the role of experimental manipulations related to theoretical questions and analysis choices. The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects. Interestingly, this ability is not modulated by age or vocabulary size, suggesting that a mature understanding of native language phonology may be present in infants from an early age, possibly before the vocabulary explosion. These results also support several theoretical assumptions made in the literature, such as sensitivity to mispronunciation size and position of the mispronunciation. We also shed light on the impact of data analysis choices that may lead to different conclusions regarding the development of infants' mispronunciation sensitivity. Our paper concludes with recommendations for improved practice in testing infants' word and sentence processing on-line.

@@

To disentangle the predictions that phono-lexical representations are progressively becoming more specified or are specified early, we investigate the relationship between mispronunciation sensitivity and age as well as vocabulary size. But, this may not account for all variability found in the literature. Indeed, different laboratories may vary in their approach to creating a mispronunciation sensitivity experiment, using different types of stimuli and methodologies. Many studies pose more nuanced questions, such as examining the impact of number of phonological features changed (mispronunciation size) or the location of the mispronunciation. Some studies may differ in their experimental design, presenting a distractor image that is either familiar or completely novel. In our meta-analysis we code for features of the experiment that are often reported but vary across studies and include an analysis of these features to shed further light on early phono-lexical representations and their maturation.

These research questions and experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete. The PRIMIR Framework (Processing Rich Information from Multidimensional Interactive Representations; Curtin \& Werker, 2007; Werker \& Curtin, 2005) describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail. The ability to access and use this detail, however, is governed by the task or developmental demands probed in a particular experiment. For example, if infants are tested on a more subtle mispronunciation that changes only one phonological feature, they may be less likely to identify the change in comparison to a mispronunciation that changes two or three phonological features (White \& Morgan, 2008). If older infants are more likely to be tested using a more demanding mispronunciation sensitivity task, this may attenuate developmental effects across studies. Note, however, that those studies reporting change (Altvater-Mackensen, 2010; Altvater-Mackensen et al., 2014; Feest \& Fikkert, 2015; Mani \& Plunkett, 2007) or no change (Bailey \& Plunkett, 2002; Swingley \& Aslin, 2000; Zesiger et al., 2012) all presented the same task across ages.

The first set of questions concern how infants' sensitivity is modulated by different kinds of mispronunciations. Following on the above example, some experiments examine infants' sensitivity to factors that change the identity of a word on a measurable level, or \emph{mispronunciation size} (i.e.~1-feature, 2-features, 3-features), finding that infants are more sensitive to larger mispronunciations (3-feature-changes) than smaller mispronunciations (1-feature changes) for both consonant (Bernier \& White, 2017; Tamasi, 2016; White \& Morgan, 2008) and vowel (Mani \& Plunkett, 2011) mispronunciations, known as graded sensitivity. This also has consequences for understanding the developmental trajectory of mispronunciation sensitivity, as adults show similar graded sensitivity (Bailey \& Hahn, 2005).

@@

A second set of questions is whether the experimental context modulates infants' responses to mispronunciations. In order to study the influence of mispronunciation position, many studies control the \emph{phonological overlap between target and distractor labels}. For example, when examining sensitivity to a vowel mispronunciation of the target word \enquote{ball}, the image of a ball would be paired with a distractor image that shares onset overlap, such as \enquote{bed}. This ensures that infants cannot use the onset of the word to differentiate between the target and distractor images (Mani \& Plunkett, 2007). Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.

@@

The models reported here are multilevel random-effects models of variance-weighted effect sizes, which we computed with the R (R Core Team, 2018) package metafor (Viechtbauer, 2010). To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we first introduced age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model. Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the package meta (Schwarzer, 2007). For a subsequent investigation of experimental characteristics, we introduced each as a moderator: size of mispronunciation, position of mispronunciation, type of mispronunciation, phonological overlap between target and distractor labels, and distractor familiarity (more detail below).

@@

In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not. Age did not significantly modulate object identification in response to correctly pronounced (QM(1) = 0.537, \emph{p} = 0.464) or mispronounced words (QM(1) = 1.663, \emph{p} = 0.197). The lack of a significant modulation together with the small estimates for age (correct: \(\beta\) = 0.014, SE = 0.019, 95\% CI{[}-0.023, 0.05{]}, \emph{p} = 0.464; mispronunciation: \(\beta\) = 0.015, SE = 0.011, 95\% CI{[}-0.008, 0.037{]}, \emph{p} = 0.197) indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label. However, previous experimental studies ((e.g.~Fernald, Pinto, Swingley, Weinberg, \& McRoberts, 1998)) and a recent meta-analysis (Frank, Lewis, \& Macdonald, 2016) have found that children's speed and accuracy in recognition of correctly pronounced words increases with age. Perhaps older children are more likely to be tested on less-frequent, later learned words than younger children, which could lead to a lack of a relationship between age and target looks in response to correct pronunciations in the current meta-analysis.

@@

Figure \ref{fig:Vocabdescribe1} plots the year of publication for all the mispronunciation sensitivity studies included in this meta-analysis. This figure illustrates two things: the increasing number of mispronunciation sensitivity studies in general and the decreasing number of mispronunciation studies measuring vocabulary. The lack of evidence for a relationship between mispronunciation sensitivity and vocabulary size in some early studies may have contributed to increasingly fewer researchers including vocabulary measurements in their mispronunciation sensitivity experimental design. This may explain our underpowered analysis of the relationship between object recognition for correct pronunciations and mispronunciations and vocabulary size, despite its theoretical interest.

@@

Our power analysis revealed that mispronunciation sensitivity studies typically underpowered, with 54\% power and would need to increase their sample from an average of 24 to 44more infants to achieve 80\% power. While this number does not seem to differ dramatically from the observed sample sizes, the impact of the smaller sample sizes on power is thus substantial and should be kept in mind when planning future studies. Furthermore, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA (Fleiss, 1986) and mixed-effect-model (Leon \& Heo, 2009) analyses. We thus strongly advocate for a consideration of power and the reported effect sizes to test infants' mispronunciation sensitivity and factors influencing this ability.

@@

We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to mispronunciations on the onset (\emph{n} = 143 records), medial medial (\emph{n} = 48), and coda phonemes (\emph{n} = 10). We coded the onset, medial, and coda positions as continuous variables, to evaluate the importance of each subsequent position (Marslen-Wilson \& Zwitserlood, 1989). We did not include data for which the mispronunciation varied within record in regard to position (\emph{n} = 40) or was not reported (\emph{n} = 10).

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotMispPosit-1.pdf}
\caption{\label{fig:PlotMispPosit}Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).}
\end{figure}

@@

We examine whether variation in the approach to data analysis may be have an influence on our conclusions regarding infants' developing mispronunciation sensitivity. To do so, we analyzed analysis choices related to timing (post-naming analysis window; offset time) and type of dependent variable in our coding of the dataset because they are consistently reported. Further, since we observe variation in both aspects of data analysis, summarizing typical choices and their impact might be useful for experiment design in the future and might help establish field standards. In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices may have on reported mispronunciation sensitivity and its development. We focus specifically on the size of the mispronunciation sensitivity effect, considering the whole dataset and including condition (correct pronunciation, mispronunciation) as a moderator.

@@

When designing mispronunciation sensitivity studies, experimenters can choose the length of time each trial is presented. This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection. Evidence suggests that the speed of word recognition processing is slower in young infants (Fernald et al., 1998), which may lead researchers to include longer post-naming phases in their experiments with younger infants. The post-naming analysis window, in contrast, represents how much of this phase was included in the statistical analysis and can be chosen after the experimental data is collected and perhaps observed. If infant age is influencing the length of these windows, we should expect a negative correlation.

@@

There was no apparent relation between infant age and post-naming phase length (\emph{r} = 0.01, 95\% CI{[}-0.11, 0.13{]}, \emph{p} = 0.882), but there was a significant negative relationship between infant age and post-naming analysis window length, such that younger infants' looking times were analyzed using a longer post-naming analysis window (\emph{r} = -0.23, 95\% CI{[}-0.35, -0.11{]}, \emph{p} \textless{} .001). Considering the post-naming analysis window may be determined after data collection and observation, we next investigated whether this impacted measures of mispronunciation sensitivity.

@@

When we included both condition and dependent variable as moderators, the moderator test was significant (QM(3) = 231.004, \emph{p} \textless{} .001). The estimate for the interaction between the type of dependent variable and condition was was significant (\(\beta\) = -0.185, SE = 0.093, 95\% CI{[}-0.366, -0.003{]}, \emph{p} = 0.046). As can be seen in @ref(fig:PlotWithinCondDV\_baseline), mispronunciation sensitivity was higher when the dependent variable reported was Post compared to when it was Baseline Corrected. When age was included as an additional moderator, the moderator test was significant (QM(7) = 237.51, \emph{p} \textless{} .001). However, the estimate for the interaction between dependent variable, condition, and age was not significant (\(\beta\) = -0.049, SE = 0.026, 95\% CI{[}-0.1, 0.002{]}, \emph{p} = 0.061).

(Insert Figure @ref(fig:PlotWithinCondDV\_baseline) about here)

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotWithinCondAgeDiffScore_old-1.pdf}
\caption{(\#fig:PlotWithinCondAgeDiffScore\_old)Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs.~Pre (blue), and Difference Score (green). Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age. The lines plot the linear regression and the gray shaded area indicates the standard error.}
\end{figure}

@@

The results of the moderator analysis reflect several findings reported in the literature. The meta-analytic effect for ispronunciation size, as measured by phonological features changed, showed graded sensitivity (Bernier \& White, 2017; Mani \& Plunkett, 2011; Tamasi, 2016; White \& Morgan, 2008), an adult-like ability. More studies are needed to evaluate whether this gradual sensitivity develops with age, as only one study examined more than one age (Mani \& Plunkett, 2011) and all others test the same age (Bernier \& White, 2017; Tamasi, 2016; White \& Morgan, 2008). With more studies investigating graded sensitivity at multiple ages in infancy, we would achieve a better estimate of whether this is a stable or developing ability, thus also shedding more light on the progression of phono-lexical development in general that then needs to be captured in theories and models.

@@

Contrary to predictions made from the literature, our meta-analysis revealed that studies which include target and distractor images that overlap in their onset elicit greater mispronunciation sensitivity than studies who do not control for this factor. Perhaps including overlap leads infants to pay more attention to mispronunciations, increasing mispronunciation sensitivity. Yet, older children were more likely to receive the arguably more difficult manipulation where target-distractor pairs overlapped in their onset phoneme, added task demands which may reduce their ability to access the phonetic detail of familiar words as argued by the PRIMIR Framework (Curtin \& Werker, 2007; Werker \& Curtin, 2005). This imbalance has the potential to dampen developmental differences, which would be hidden by task differences in the experiments that older and younger infants participated in. Further support comes from evidence that sensitivity to mispronunciations when the target-distractor pair overlapped on the onset phoneme increased with age. This pattern of results suggests that when infants are given an equally difficult task, developmental effects may be revealed. This explanation can be confirmed by testing more young infants on overlapping target-distractor pairs.

@@

During the coding of our meta-analysis database, we noted variation in variables relating to timing and the calculation of the dependent variable reported. As infants mature, they recognize words more quickly (Fernald et al., 1998), which may lead experimenters to adjust and lower offset times in their analysis as well as shorten the length of the analysis window. A majority of studies used an offset time between 360 and 370 ms (\emph{n} = 151), which follows the \enquote{best guess} of Swingley \& Aslin (2000) for the amount of time needed for infants to initiate eye movements in response to a spoken target word; in contrast, we found wide variation in the post-naming analysis window which correlated negatively with infant age and influenced the estimate of mispronunciation sensitivity. Looks to the target in response to mispronunciations may be slower than that of correct pronunciations in infants (as predicted by TRACE, Mayor \& Plunkett, 2014), and those studies with longer post-naming analysis windows capture this effect, thereby reducing the measured sensitivity to mispronunciations. Although we have no direct evidence, an analysis window can be potentially set after collecting data. At worst, this adjustment could be the result of a desire to confirm a hypothesis, increasing the rate of false-positives (Gelman \& Loken, 2013): a \enquote{significant effect} of mispronunciation sensitivity is found with an analysis window of 2000 but not 3000 ms, therefore 2000 ms is chosen. At best, this variation introduces noise into the study of mispronunciation sensitivity, blurring the true developmental trajectory of mispronunciation sensitivity.

The type of depedent variable calculated also moderated mispronunciation sensitivity, albeit not conclusions about its developmental trajectory. Unlike the exploratory analyses related to timing, there is no clear reason for one dependent variable to be chosen over another; the prevalence of each dependent variable appears distributed across ages and some authors always calculate the same dependent variable while others use them interchangeably in different publications. One clear difference is that both the Difference Score (reporting looks to the target image after hearing the label minus looks in silence) and Pre vs.~Post (reporting both variables separately) dependent variables consider each infants' actual preference in the pre-naming baseline phase, while the Post dependent variable (reporting looks to target after labelling only) does not. Without access to the raw data, it is difficult to conclusively determine why different dependent variable calculations influence mispronunciation sensitivity.

@@

This meta-analysis comprises an aggregation of two decades of research on mispronunciation sensitivity, finding robust evidence that infants have well-specified phonological representations for familiar words. Furthermore, these representations may be well specified at an early age, perhaps before the vocabulary explosion. We recommend future theoretical frameworks take this evidence into account. Our meta-analysis was also able to confirm different findings in the literature, including the role of mispronunciation size, mispronunciation position, and the role of age and native language in sensitivity to mispronunciation type (consonant vs.~vowel). Furthermore, evidence of an interaction between task demands (phonological overlap between target-distractor pairs) and infant age may partially explain the lack of developmental change in our meta-analysis.

Despite this overall finding, we note evidence that data analysis choices can modulate conclusions about mispronunciation sensitivity development. Future studies should be carefully planned with this evidence in mind. Ideally, future experimental design and data analysis would become standardized which will be aided by the growing trend of preregistration and open science practices. Our analysis highlights how meta-analyses can aid in identification of issues in a particular field and play a vital role in how the field addresses such issues.

>>>>

\abstract{
As they develop into mature speakers of their native language, infants must not only learn words but also the sounds that make up those words. To do so, they must strike a balance between accepting speaker dependent variation (e.g.~mood, voice, accent), but appropriately rejecting variation when it (potentially) changes a word's meaning (e.g.~cat vs.~hat). This meta-analysis focuses on studies investigating infants' ability to detect mispronunciations in familiar words, or mispronunciation sensitivity. Our goal was to evaluate the development of infants' phonological representations for familiar words as well as explore the role of experimental manipulations related to theoretical questions and of analysis choices. The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects. Interestingly, this ability is not modulated by age or vocabulary size, suggesting that a mature understanding of native language phonology may be present in infants from an early age, possibly before the vocabulary explosion. These results support several theoretical assumptions made in the literature, such as sensitivity to mispronunciation size and position of the mispronunciation. We also shed light on the impact of data analysis choices that may lead to different conclusions regarding the development of infants' mispronunciation sensitivity. Our paper concludes with recommendations for improved practice in testing infants' word and sentence processing on-line.

@@

To disentangle the predictions that phono-lexical representations are progressively becoming more specified or are specified early, we investigate the relationship between mispronunciation sensitivity and age as well as vocabulary size by aggregating 20 years of mispronunciation sensitivity studies. But, this may not account for all variability found in the literature. Indeed, different laboratories may vary in their approach to creating a mispronunciation sensitivity experiment, using different types of stimuli and methodologies. Many studies pose more nuanced questions, such as examining the impact of number of phonological features changed (mispronunciation size) or the location of the mispronunciation. Some studies may differ in their experimental design, presenting a distractor image that is either familiar or completely novel. In our meta-analysis we code for features of the experiment that are often reported but vary across studies and include an analysis of these features to shed further light on early phono-lexical representations and their maturation.

These research questions and experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete. The PRIMIR Framework (Processing Rich Information from Multidimensional Interactive Representations; Curtin \& Werker, 2007; Werker \& Curtin, 2005) describes how infants learn to organize the incoming speech signal into phonetic and indexical detail. The ability to access and use this detail, however, is governed by the task or developmental demands probed in a particular experiment. For example, if infants are tested on a more subtle mispronunciation that changes only one phonological feature, they may be less likely to identify the change in comparison to a mispronunciation that changes two or three phonological features (White \& Morgan, 2008). If older infants are more likely to be tested using a more demanding mispronunciation sensitivity task, this may attenuate developmental effects across studies. Note, however, that those studies we reviewed above reporting change (Altvater-Mackensen, 2010; Altvater-Mackensen et al., 2014; Feest \& Fikkert, 2015; Mani \& Plunkett, 2007) or no change (Bailey \& Plunkett, 2002; Swingley \& Aslin, 2000; Zesiger et al., 2012) all presented the same task across ages.

The first set of questions concerns how infants' sensitivity is modulated by different kinds of mispronunciations. Following on the above example, some experiments examine infants' sensitivity to factors that change the identity of a word on a measurable level, or \emph{mispronunciation size} (i.e.~1-feature, 2-features, 3-features), finding that infants are more sensitive to larger mispronunciations (3-feature-changes) than smaller mispronunciations (1-feature changes) for both consonant (Bernier \& White, 2017; Tamasi, 2016; White \& Morgan, 2008) and vowel (Mani \& Plunkett, 2011) mispronunciations, known as graded sensitivity. This also has consequences for understanding the developmental trajectory of mispronunciation sensitivity, as adults show similar graded sensitivity (Bailey \& Hahn, 2005).

@@

A second set of questions is whether the experimental context modulates infants' responses to mispronunciations. In order to study the influence of mispronunciation position, many studies control the \emph{phonological overlap between target and distractor labels}. For example, when examining sensitivity to a vowel mispronunciation of the target word \enquote{ball}, the image of a ball would be paired with a distractor image that shares onset overlap, such as \enquote{bed}, as opposed to a distractor image that does not share onset overlap, such as \enquote{truck}. This ensures that infants cannot use the onset of the word to differentiate between the target and distractor images (Mani \& Plunkett, 2007). Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.

@@

The models reported here are multilevel random-effects models of variance-weighted effect sizes, which we computed with the R (R Core Team, 2018) package metafor (Viechtbauer, 2010). To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we first introduced age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model. Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the package meta (Schwarzer, 2007). For a subsequent investigation of experimental characteristics, we introduced each separately as a moderator: size of mispronunciation, position of mispronunciation, type of mispronunciation, phonological overlap between target and distractor labels, and distractor familiarity (more detail below).

@@

In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not. Age did not significantly modulate object identification in response to correctly pronounced (QM(1) = 0.537, \emph{p} = 0.464) or mispronounced words (QM(1) = 1.663, \emph{p} = 0.197). The lack of a significant modulation together with the small estimates for age (correct: \(\beta\) = 0.014, SE = 0.019, 95\% CI{[}-0.023, 0.05{]}, \emph{p} = 0.464; mispronunciation: \(\beta\) = 0.015, SE = 0.011, 95\% CI{[}-0.008, 0.037{]}, \emph{p} = 0.197) indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label. However, previous experimental studies (e.g.~Fernald, Pinto, Swingley, Weinberg, \& McRoberts, 1998) and a recent meta-analysis (Frank, Lewis, \& Macdonald, 2016) have found that children's speed and accuracy in recognition of correctly pronounced words increases with age. Perhaps older children are more likely to be tested on less-frequent, later learned words than younger children, which could lead to a lack of a relationship between age and target looks in response to correct pronunciations in the current meta-analysis.

@@

Figure \ref{fig:Vocabdescribe1} plots the year of publication for all the mispronunciation sensitivity studies included in this meta-analysis. This figure illustrates two things: the increasing number of mispronunciation sensitivity studies in general and the decreasing number of mispronunciation studies measuring vocabulary. This decrease in mispronunciation sensitivity studies measuring and reporting vocabulary size correlations is surprising, considering its theoretical interest.

@@

Our power analysis revealed that mispronunciation sensitivity studies typically underpowered, with 54\% power and would need to increase their sample from an average of 24 to 44 infants to achieve 80\% power. While this number does not seem to differ dramatically from the observed sample sizes, the impact of the smaller sample sizes on power is thus substantial and should be kept in mind when planning future studies. Furthermore, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA (Fleiss, 1986) and mixed-effect-model (Leon \& Heo, 2009) analyses. We thus strongly advocate for a consideration of power and the reported effect sizes to test infants' mispronunciation sensitivity and factors influencing this ability.

@@

We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to mispronunciations on the onset (\emph{n} = 143 records), medial (\emph{n} = 48), and coda phonemes (\emph{n} = 10). We coded the onset, medial, and coda positions as continuous variables, to evaluate the importance of each subsequent position (Marslen-Wilson \& Zwitserlood, 1989). We did not include data for which the mispronunciation varied within record in regard to position (\emph{n} = 40) or was not reported (\emph{n} = 10).

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotMispPosit-1.pdf}
\caption{\label{fig:PlotMispPosit}Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions. The dashed line indicates zero (chance).}
\end{figure}

@@

We examine whether variation in the approach to data analysis may be have an influence on our conclusions regarding infants' developing mispronunciation sensitivity. To do so, we analyzed analysis choices related to timing, specifically the post-naming analysis window, as well as type of dependent variable in our coding of the dataset because they are consistently reported. Further, since we observe variation in both aspects of data analysis, summarizing typical choices and their impact might be useful for experiment design in the future and might help establish field standards. In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices may have on reported mispronunciation sensitivity and its development. We focus specifically on the size of the mispronunciation sensitivity effect, considering the whole dataset and including condition (correct pronunciation, mispronunciation) as a moderator.

@@

When designing mispronunciation sensitivity studies, experimenters can choose the length of time each trial is presented. This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection. Evidence suggests that the speed of word recognition is slower in young infants (Fernald et al., 1998), which may lead researchers to include longer post-naming phases in their experiments with younger infants. The post-naming analysis window, in contrast, represents how much of this phase was included in the statistical analysis and can be chosen after the experimental data is collected and perhaps observed. If infant age is influencing the length of these windows, we should expect a negative correlation.

@@

There was no apparent relation between infant age and post-naming phase length (\emph{r} = 0.01, 95\% CI{[}-0.11, 0.13{]}, \emph{p} = 0.882), but there was a significant negative relationship between infant age and post-naming analysis window length, such that younger infants' looking times were analyzed using a longer post-naming analysis window (\emph{r} = -0.23, 95\% CI{[}-0.35, -0.11{]}, \emph{p} \textless{} .001). We next investigated whether post-naming analysis window length impacted measures of mispronunciation sensitivity.

@@

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotWithinCondDVbaseline-1.pdf}
\caption{\label{fig:PlotWithinCondDVbaseline}Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs.~Pre (blue), and Difference Score (green). Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age. The lines plot the linear regression and the gray shaded area indicates the standard error.}
\end{figure}

When we included both condition and dependent variable as moderators, the moderator test was significant (QM(3) = 231.004, \emph{p} \textless{} .001). The estimate for the interaction between the type of dependent variable and condition was was significant (\(\beta\) = -0.185, SE = 0.093, 95\% CI{[}-0.366, -0.003{]}, \emph{p} = 0.046). As can be seen in \ref{fig:PlotWithinCondDVbaseline}, mispronunciation sensitivity was higher when the dependent variable reported was Post compared to when it was Baseline Corrected. When age was included as an additional moderator, the moderator test was significant (QM(7) = 237.51, \emph{p} \textless{} .001). However, the estimate for the interaction between dependent variable, condition, and age was not significant (\(\beta\) = -0.049, SE = 0.026, 95\% CI{[}-0.1, 0.002{]}, \emph{p} = 0.061).

(Insert Figure \ref{fig:PlotWithinCondDVbaseline} about here)

@@

The results of the moderator analysis reflect several findings reported in the literature. The meta-analytic effect for mispronunciation size, as measured by phonological features changed, showed graded sensitivity (Bernier \& White, 2017; Mani \& Plunkett, 2011; Tamasi, 2016; White \& Morgan, 2008), an adult-like ability. More studies are needed to evaluate whether this gradual sensitivity develops with age, as only one study examined more than one age (Mani \& Plunkett, 2011) and all others test the same age with a varying number of features (Bernier \& White, 2017; Tamasi, 2016; White \& Morgan, 2008). With more studies investigating graded sensitivity at multiple ages with all other facturs held constant, we would achieve a better estimate of whether this is a stable or developing ability, thus also shedding more light on the progression of phono-lexical development in general that then needs to be captured in theories and models.

@@

Contrary to predictions made from the literature, our meta-analysis revealed that studies which include target and distractor images that overlap in their onset elicit greater mispronunciation sensitivity than studies who do not control for this factor. Perhaps including overlap leads infants to pay more attention to mispronunciations, increasing mispronunciation sensitivity. Yet, older children were more likely to receive the arguably more difficult manipulation where target-distractor pairs overlapped in their onset phoneme, added task demands which may reduce their ability to access the phonetic detail of familiar words as argued by the PRIMIR Framework (Curtin \& Werker, 2007; Werker \& Curtin, 2005). This imbalance in the ages tested has the potential to dampen developmental differences, due to task differences in the experiments that older and younger infants participated in. Further support comes from evidence that sensitivity to mispronunciations when the target-distractor pair overlapped on the onset phoneme increased with age. This pattern of results suggests that when infants are given an equally difficult task, developmental effects may be revealed. This explanation can be confirmed by testing more infants at younger ages on overlapping target-distractor pairs in the future.

@@

During the coding of our meta-analysis database, we noted variation in variables relating to timing and the calculation of the dependent variable reported. As infants mature, they recognize words more quickly (Fernald et al., 1998), which may lead experimenters to shorten the length of the analysis window. We found wide variation in the post-naming analysis window which correlated negatively with infant age and influenced the estimate of mispronunciation sensitivity. Looks to the target in response to mispronunciations may be slower than in response to correct pronunciations in infants (as predicted by TRACE, Mayor \& Plunkett, 2014), and those studies with longer post-naming analysis windows allow fixations to accumulate even in the presence of mispronunciations, thereby reducing the measured sensitivity to mispronunciations. In fact, the exact dynamics of fixations to mispronunciations (overall flattened versus delayed) are an ongoing topic of discussion. Returning to the analysis window length itself, we wish to raise awareness that the observed variation might seem like it indicates a so-called Questionable Research Practice where analyses are adjusted after observing the data to obtain a significant effect, which in turn increases the rate of false-positives (Gelman \& Loken, 2013): a \enquote{significant effect} of mispronunciation sensitivity is found with an analysis window of 2000 but not 3000 ms, therefore 2000 ms is chosen. While we have no reason to believe that this is the cause of the observed variation, consistency or justification of chosen time windows would increase the credibility of developmental eye movement research. In addition, and even in the absence of such practices, the variation in analysis window length introduces noise into the dataset, blurring the true developmental trajectory of mispronunciation sensitivity.

The type of depedent variable calculated also moderated mispronunciation sensitivity, albeit not conclusions about its developmental trajectory. There is, to the best of our knowledge, no clear reason for one dependent variable to be chosen over another; the prevalence of each dependent variable appears distributed across ages and some authors always calculate the same dependent variable while others use them interchangeably in different publications. One clear difference is that both the Difference Score (reporting looks to the target image after hearing the label minus looks in silence) and Pre vs.~Post (reporting both variables separately) dependent variables consider each infants' actual preference in the pre-naming baseline phase, while the Post dependent variable (reporting looks to target after labelling only) does not. Without access to the raw data, it is difficult to conclusively determine why different dependent variable calculations influence mispronunciation sensitivity.

@@

This meta-analysis comprises an aggregation of two decades of research on mispronunciation sensitivity, finding robust evidence that infants have well-specified phonological representations for familiar words. Furthermore, these representations may be well specified at an early age, perhaps before the vocabulary explosion. We recommend future theoretical frameworks take this evidence into account. Our meta-analysis was also able to confirm different findings in the literature, including the role of mispronunciation size, mispronunciation position, and infants' age and native language in sensitivity to mispronunciation type (consonant vs.~vowel). Furthermore, evidence of an interaction between task demands (phonological overlap between target-distractor pairs) and infant age may partially explain the lack of developmental change in our meta-analysis.

Despite this overall finding, we note evidence that data analysis choices can modulate conclusions about mispronunciation sensitivity development. Future studies should be carefully planned with this evidence in mind. Ideally, future experimental design and data analysis would become standardized which will be aided by the growing trend of preregistration and open science practices. Our analysis highlights how meta-analyses can identify issues in a particular field and play a vital role in how the field addresses such issues.
